The ChEMBL database as Linked Open Data

### 2012-03-01 article.tex
Added Ola as author
Test commit by SSH
Some further content...

% Two or more authors:
%\author[A]{\fnms{} \snm{}\thanks{}},
%\author[B]{\fnms{} \snm{}}
%\runningauthor{}
%\address[A]{}
%\address[B]{}

@@

@@

Ola: use in BC-DS for possible adverse reactions

@@

@@

%\begin{table*}
%\caption{} \label{t1}
%\begin{tabular}{lll}
%\hline
%&&\\
%&&\\
%\hline
%\end{tabular}
%\end{table*}

@@

\printbibliography

>>>>

% Two or more authors:
\author[A]{\fnms{Ola} \snm{Spjuth}\thanks{}},
%\author[B]{\fnms{} \snm{}}
%\runningauthor{}
%\address[A]{}
%\address[B]{}

@@

Throughout this paper, various prefixes are used to simplify RDF output, outlined
in Table~\ref{namespaces}.

@@

Ola: Use in BC-DS for possible adverse reactions.

@@

\begin{small}
\begin{verbatim}
act:a31863
      a       chembl:Activity ;
      cito:citesAsDataSource
              res:r6424 ;
      chembl:forMolecule mol:m180094 ;
      chembl:onAssay assay:a54505 ;
      chembl:relation ">" ;
      chembl:standardUnits
              "nM" ;
      chembl:standardValue
              "100000"^^xsd:float ;
      chembl:type "IC50" .
\end{verbatim}
\end{small}

@@

\begin{table*}
\caption{Prefixes and their matching namespaces used in this paper.} \label{namespaces}
\begin{tabular}{ll}
\hline
Common & Vocabularies \\
cito & Citation Typing Ontology~\cite{ont:cito} \\
     & http://purl.org/spar/cito/ \\

\hline
ChEMBL-RDF & Namespaces\\
act    & http://data.kasabi.com/dataset/chembl-rdf/activity/ \\
chembl & http://rdf.farmbio.uu.se/chembl/onto/\# \\
res    & http://data.kasabi.com/dataset/chembl-rdf/resource/ \\
assay  & http://data.kasabi.com/dataset/chembl-rdf/assay/ \\
mol    & http://data.kasabi.com/dataset/chembl-rdf/molecule/ \\
\hline
\end{tabular}
\end{table*}

@@

% \printbibliography
